---
title: "MTA Permanent Art Catalog"
subtitle: "TidyTuesday 2025-07-22"
date: "2025-07-22"
author: "Aaron Wright"
categories: [r, ggplot2, tidyverse, data-viz]
image: "plot.svg"
---

<!-- THEMATICS AND RENDERING -->

::: cell

```{=html}
<style>
/* inline code */
code {
  background-color: #f5f5f5;
  color: #859901; /* solarized green */
  border-radius: 4px;
  padding: 2px 4px;
  font-family: monospace;
  font-size: 0.95em;
}

/* list item spacing for inline code */
li code {
  margin-left: 2px;
}

/* link styling */
a {
  color: #2AA198; /* solarized cyan */
  text-decoration: none;
}
a:hover {
  text-decoration: underline;
}
</style>
```
:::

<!-- CONFIGURATION -->

## Overview
---
This week's TidyTuesday challenge focused on [DATASET_DESCRIPTION]. I explored [KEY_INSIGHTS] using r to [VISUALIZATION_APPROACH].

> **Key Libraries**: ggplot2, dplyr, tidyr <br>

<!-- ENVIRONMENT & DATA -->

## Dataset
---
The dataset for this week included [DATASET_FEATURES].

> **Source:** [MTA Permanent Art Catalog: Beginning 1980](https://data.ny.gov/Transportation/MTA-Permanent-Art-Catalog-Beginning-1980/4y8j-9pkd/about_data) <br>
> **Article:** [Permanent Art](https://www.mta.info/agency/arts-design/permanent-art) <br>

### Import
```{r}
#| label: load-data
#| message: false
#| warning: false

# Load required libraries
{{LIBRARY_IMPORTS}}
library(tidytuesdayR)
library(tidyverse)
library(here)

# R
source("load_tidytuesday_data.R")
tidytuesday_data <- prepare_tidytuesday_data("2025-07-22")
```

### Structure

```{r}
#| label: explore-data

# Examine the dataset
{{DATA_EXPLORATION}}
```

<!-- WRANGLING & ANALYSIS -->

## Analysis
---
### Cleaning

```{r}
#| label: prep-data

# Clean and prepare the data (script provided by tidytuesday community)
{{DATA_PREPARATION}}
# Clean data provided by the State of New York's data.ny.gov. No cleaning was
# necessary. We split off the station_lines dataset as a demonstration.

mta_art <- readr::read_csv("https://data.ny.gov/resource/4y8j-9pkd.csv")

station_lines <- mta_art |>
  dplyr::select("agency", "station_name", "line") |>
  dplyr::filter(!is.na(.data$line)) |>
  tidyr::separate_longer_delim("line", ",")

```

## Plotting
---

```{r}
#| label: main-plot
#| fig-width: 12
#| fig-height: 8
#| warning: false

# Create the main visualization
{{MAIN_VISUALIZATION}}
```
<!-- VISUALIZATION & COMMENTARY -->

## Technical Summary
---
- **Data Source**: [TidyTuesday GitHub Repository](https://github.com/rfordatascience/tidytuesday)
- **Analysis Date**: 2025-07-22
- **Tools Used**: R, ggplot2, tidyverse
- **Key Libraries**: ggplot2, dplyr, tidyr

## Vizualization
---
![]({IMAGE_FILE})

## Future Directions
---
- [POTENTIAL_IMPROVEMENTS]
- [FUTURE_ANALYSIS_IDEAS]
- [DATA_QUALITY_NOTES]

<!-- CITATIONS -->

## TidyTuesday
---
> **Official Tidy Tuesday Repository**: [tidytuesday](https://github.com/rfordatascience/tidytuesday) <br>
> **{tidytuesdayR} Package Repository**: [tidytuesdayR](https://github.com/dslc-io/tidytuesdayR) <br>
> **CRAN Package**: [CRAN: Package tidytuesdayR](https://CRAN.R-project.org/package=tidytuesdayR) <br>
> **References** @tidytuesday, @tidytuesdayR