---
title: "MTA Permanent Art Catalog"
subtitle: "TidyTuesday 2025-07-22"
date: "2025-07-22"
author: "Aaron Wright"
categories: [r, ggplot2, tidyverse, data-viz]
image: "plot.svg"
---

<!-- THEMATICS AND RENDERING -->

::: cell

```{=html}
<style>
/* inline code */
code {
  background-color: #f5f5f5;
  color: #859901; /* solarized green */
  border-radius: 4px;
  padding: 2px 4px;
  font-family: monospace;
  font-size: 0.95em;
}

/* list item spacing for inline code */
li code {
  margin-left: 2px;
}

/* link styling */
a {
  color: #2AA198; /* solarized cyan */
  text-decoration: none;
}
a:hover {
  text-decoration: underline;
}
</style>
```
:::

<!-- CONFIGURATION -->

## Overview
---
This week's TidyTuesday challenge focused on [DATASET_DESCRIPTION]. I explored [KEY_INSIGHTS] using r to [VISUALIZATION_APPROACH], asking **do specific agencies tend to attract certain types of art materials?**

My visualization for this challenge was specifically influenced by Cédric Scherer's contribution to the 2020 week 12 challenge (find it [here](https://github.com/z3tt/TidyTuesday/blob/main/R/2020_12_TheOffice.Rmd)), in which he visualized ratings of The Office.

> **Key Libraries**: ggplot2, dplyr, tidyr <br>

<!-- ENVIRONMENT & DATA -->

## Dataset
---
The dataset for this week included [DATASET_FEATURES].

> **Source:** [MTA Permanent Art Catalog: Beginning 1980](https://data.ny.gov/Transportation/MTA-Permanent-Art-Catalog-Beginning-1980/4y8j-9pkd/about_data) <br>
> **Article:** [Permanent Art](https://www.mta.info/agency/arts-design/permanent-art) <br>

### Import
```{r}
#| label: load-data
#| message: false
#| warning: false

# Load required libraries
library(tidytuesdayR)
library(tidyverse)
library(here)
library(visdat)


# R
source("load_tidytuesday_data.R")
tidytuesday_data <- prepare_tidytuesday_data("2025-07-22")
```

### Structure

```{r}
#| label: explore-data

# Examine the dataset
vis_dat(mta_art)
vis_dat(station_lines)

# mta_art
print(unique(mta_art$agency))
print(unique(mta_art$art_material))
```

<!-- WRANGLING & ANALYSIS -->

## Analysis
---
### Cleaning

```{r}
#| label: prep-data

# Clean and prepare the data
{{DATA_PREPARATION}}

```

### Art by material

```{r}
#| label: curation

```

## Plotting
---

```{r}
#| label: main-plot
#| fig-width: 12
#| fig-height: 8
#| warning: false

# Create the main visualization

# evolution of materials in art debuts by different agencies over time
# 6 line plots, vertically (axes flipped) with year on the y, agency groupings on x
# coloring points by material - requires a bit of configuration with regex
# interactive to have points reflect art descriptions?

mta_art %>%
  group_by(agency) %>%
  ggplot(aes(x = agency, y = art_date), color = agency) +
  geom_line()

```
<!-- VISUALIZATION & COMMENTARY -->

## Technical Summary
---
- **Data Source**: [TidyTuesday GitHub Repository](https://github.com/rfordatascience/tidytuesday)
- **Analysis Date**: 2025-07-22
- **Tools Used**: R, ggplot2, tidyverse
- **Key Libraries**: ggplot2, dplyr, tidyr

## Vizualization
---
![]({IMAGE_FILE})

## Future Directions
---
- [POTENTIAL_IMPROVEMENTS]
- [FUTURE_ANALYSIS_IDEAS]
- [DATA_QUALITY_NOTES]

<!-- CITATIONS -->

## TidyTuesday
---
> **Official Tidy Tuesday Repository**: [tidytuesday](https://github.com/rfordatascience/tidytuesday) <br>
> **{tidytuesdayR} Package Repository**: [tidytuesdayR](https://github.com/dslc-io/tidytuesdayR) <br>
> **CRAN Package**: [CRAN: Package tidytuesdayR](https://CRAN.R-project.org/package=tidytuesdayR) <br>
> **References** @tidytuesday, @tidytuesdayR