---
title: "MTA Permanent Art Catalog"
subtitle: "TidyTuesday "
date: ""
author: "Aaron Wright"
categories: [r, ggplot2, tidyverse, data-viz]
image: "plot.svg"
---

## Overview

This week's TidyTuesday focused on [DATASET_DESCRIPTION]. I explored [KEY_INSIGHTS] using r to [VISUALIZATION_APPROACH].

## Dataset

```{r}
#| label: load-data
#| message: false
#| warning: false

# Get data
library(tidytuesdayR)
dat <- tt_load("")

# Load other required libraries
{{LIBRARY_IMPORTS}}

```

### Data Structure

```{r}
#| label: explore-data

# Examine the dataset
{{DATA_EXPLORATION}}
```

## Analysis

### Data Preparation

```{r}
#| label: prep-data

# Clean and prepare the data
{{DATA_PREPARATION}}
```

## Visualization

```{r}
#| label: main-plot
#| fig-width: 12
#| fig-height: 8
#| warning: false

# Create the main visualization
{{MAIN_VISUALIZATION}}
```

## Technical Notes

- **Data Source**: [TidyTuesday GitHub Repository](https://github.com/rfordatascience/tidytuesday)
- **Analysis Date**: 
- **Tools Used**: R, ggplot2, tidyverse
- **Key Libraries**: ggplot2, dplyr, tidyr

## Viz

![]({IMAGE_FILE})

## Next Steps

- [POTENTIAL_IMPROVEMENTS]
- [FUTURE_ANALYSIS_IDEAS]
- [DATA_QUALITY_NOTES]
