---
title: "Netflix Views"
subtitle: "TidyTuesday 2025-07-29"
date: "2025-07-29"
author: "Aaron Wright"
categories: [r, ggplot2, tidyverse, data-viz]
image: "plot.svg"
---

<!-- THEMATICS AND RENDERING -->

::: cell

```{=html}
<style>
/* inline code */
code {
  background-color: #f5f5f5;
  color: #859901; /* solarized green */
  border-radius: 4px;
  padding: 2px 4px;
  font-family: monospace;
  font-size: 0.95em;
}

/* list item spacing for inline code */
li code {
  margin-left: 2px;
}

/* link styling */
a {
  color: #2AA198; /* solarized cyan */
  text-decoration: none;
}
a:hover {
  text-decoration: underline;
}
</style>
```
:::

<!-- CONFIGURATION -->

## Overview
---
This week's TidyTuesday challenge focused on [DATASET_DESCRIPTION]. I explored [KEY_INSIGHTS] using r to [VISUALIZATION_APPROACH], asking [RESEARCH_QUESTION]

> **Key Libraries**: ggplot2, dplyr, tidyr <br>

<!-- ENVIRONMENT & DATA -->

## Dataset
---
The dataset for this week included [DATASET_FEATURES].

> **Source:** [Info](Link) <br>
> **Article:** [What We Watched the First Half of 2025](https://about.netflix.com/en/news/what-we-watched-the-first-half-of-2025) <br>

### Import
```{r}
#| label: load-data
#| message: false
#| warning: false

# Load required libraries
library(tidytuesdayR)
library(tidyverse)
library(here)
library(readxl)
library(janitor)

# Get data (script provided by tidytuesday community)
# R
source("load_tidytuesday_data.R")
tidytuesday_data <- prepare_tidytuesday_data("2025-07-29")

```

### Structure

```{r}
#| label: explore-data

# Examine the dataset
{{DATA_EXPLORATION}}
```

<!-- WRANGLING & ANALYSIS -->

## Analysis
---
### Cleaning

```{r}
#| label: prep-data

# Clean and prepare the data

```

## Plotting
---

```{r}
#| label: main-plot
#| fig-width: 12
#| fig-height: 8
#| warning: false

# Create the main visualization
{{MAIN_VISUALIZATION}}
```
<!-- VISUALIZATION & COMMENTARY -->

## Technical Summary
---
- **Data Source**: [TidyTuesday GitHub Repository](https://github.com/rfordatascience/tidytuesday)
- **Analysis Date**: 2025-07-29
- **Tools Used**: R, ggplot2, tidyverse
- **Key Libraries**: ggplot2, dplyr, tidyr

## Vizualization
---
![]({IMAGE_FILE})

## Future Directions
---
- [POTENTIAL_IMPROVEMENTS]
- [FUTURE_ANALYSIS_IDEAS]
- [DATA_QUALITY_NOTES]

<!-- CITATIONS -->

## TidyTuesday
---
> **Official Tidy Tuesday Repository**: [tidytuesday](https://github.com/rfordatascience/tidytuesday) <br>
> **{tidytuesdayR} Package Repository**: [tidytuesdayR](https://github.com/dslc-io/tidytuesdayR) <br>
> **CRAN Package**: [CRAN: Package tidytuesdayR](https://CRAN.R-project.org/package=tidytuesdayR) <br>
> **References** @tidytuesday, @tidytuesdayR